%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-1em}
\section{Education}

\cventry{2021--2023}{Master's Mechanical Engineering}{University College Dublin}{}{Award GPA: 3.34}{Relevant Modules: 
Fluid Mechanics III, 
Mechanics of Solids III, 
Process Control, 
%Professional Engineering (Management),
Numerical Algorithms,
Fracture Mechanics,
Computational Continuum Mechanics II,
Engineering Thermodynamics III,
%Manufacturing Engineering II,
Energy Systems and Climate Change,
\newline Dissertation: Optimising the Hybrid Operation Temperature Window of a Hybrid Heating System (air-to-water heat pump + gas boiler) in the Irish Climate \href{https://github.com/daniel-jakob/Thesis}{[GitHub]} \href{https://www.jakob.ie/assets/thesis/jakob_daniel_FinalReport_ReSubmission.pdf}{[PDF]}.} % Arguments not required can be left empty
\cventry{2018--2021}{BSc. Mechanical Engineering}{University College Dublin}{}{Award GPA: 3.66}{Relevant Modules: 
Material Science II, 
%Electrical Energy Systems ,
Applied Dynamics II,
Multivariable Calculus Eng II ,
Mechanical Engineering Design II,
% Measurement \& Instrumentation,
Heat Transfer,
Linear Algebra for Engineers,
Statistics \& Probability,
Modelling \& Simulation, 
Comp. Sci. for Engineers II,\newline 
Projects: Rotating Disc Electrodeposition Device with Ultrasonic Agitation design group project. Skills developed: CAD Skills, Presenation skills and animation/directing skills.}
\cventry{2012--2018}{Secondary School}{Presentation College}{Bray}{\textit{Leaving Cert. Points -- 543}}{H1 -- German, H2 -- Design Communication Graphics, Physics, Geography.}  % Arguments not required can be left empty
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\cventry{Jan 2022 -- Aug 2022}{Engineering Intern}{\textsc{Jones Engineering}}{Intel Campus, Leixlip}{}{Aided tradesmen on-site by navigating the 3D Navisworks digital twin model of the Fab34 site. Created many tools to help the engineering team, in particular, a comprehensive search-engine-like tool and accompanying interface that merged data from four sources, significantly reducing time required to get info on a particular pipe/duct. Led a data-science-driven investigation into missing isometric drawing files, developing a large data model in PowerQuery and PowerBI.}

\cventry{Jun 2021 -- Dec 2021}{Part-Time Waiter}{\textsc{Boomerang Bar}}{Bray}{}{Part-time waitering staff at a family owned wet pub. Tasks included: serving drinks to customers, money collection, daily set-up and cleaning.}

\cventry{Oct 2018 -- Mar 2020}{Part-Time Waiter}{\textsc{Lana Asian Street Food}}{Bray}{}{Created and developed an Excel spreadsheet which sped up end-of-day closing dramatically. Part-time waiter in an Asian/Thai food restaurant chain. Tasks included: waitering service, end-of-day cash register balancing, cleaning, coffee making, cashiering, taking in and signing off wholesale deliveries, dealing with customer complaints and on occasion, managing the floor. Shared a key to the premises with a fellow part-time waiter.}

\cventry{Aug 2018}{Attendant}{\textsc{Hell-\&-Back}}{}{}{Guided participants and supervisor for a weekend at Hell-\&-Back as an attendant in the car park and the course.}

\cventry{Jun 2017}{Attendant}{\textsc{Junior \& Leaving Cert}}{}{}{3 weeks worked as a Junior and Leaving Cert. attendant in Presentation College.}



%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitem{2022}{Safe Pass construction site permit} 
\cvitem{2021}{IACT Working Safely For Employees in Pubs Cert. and Manual Handling Thoery}
\cvitem{2018}{Lifeguard Rescue Level 3 Award}
\cvitem{2018}{First Aid training course and BLS training}
\cvitem{2017, 2018}{5\textsuperscript{th} and 6\textsuperscript{th} year Academic Excellence in German}
\cvitem{2017}{Level 3 Kayaking Award}
\cvitem{2016}{Level 2 Diving Award}
\cvitem{2013--2017}{$3\times$ Spirit of Pres Award}
\cvitem{2012--2018}{$3\times$ Excellent Attendance Award}



%\newpage

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Basic}{\texttt{JavaScript}/\texttt{JQuery}, Adobe Photoshop, \texttt{PHP}, \texttt{SQL}, \texttt{R}, \texttt{AHK}, Docker, \texttt{C} \& \texttt{\CC}}
\cvitem{Intermediate}{SolidWorks, Autodesk Inventor, \texttt{HTML}, \texttt{CSS}, \texttt{Git}, (Arch) Linux, PowerQuery+\texttt{M}-code, PowerBI, \texttt{EnergyPlus}, \texttt{Python}+Jupyter Notebooks}
\cvitem{Advanced}{\LaTeX+friends, Excel+\texttt{VBA}, \texttt{MATLAB}, \texttt{Modelica}}

%----------------------------------------------------------------------------------------
%	RECENT PROJECTS
%----------------------------------------------------------------------------------------

\section{Recent Dev. Projects}

\cvitem{\texttt{Python}}{\href{https://github.com/daniel-jakob/Bottle_Cap_Map}{[Link]} Features: numerical optimisation, API calls, computer vision, geospatial interpolation, geometric transformations, automated unittesting with GitHub CI/CD.}
\cvitem{\texttt{Python}}{\href{https://github.com/daniel-jakob/egg_missions}{[Link]} Features: API requests and reponses, data manipulation and interpretation, data visualisation via composite image generation}
\cvitem{CI/CD}{\href{https://github.com/daniel-jakob/EggIncProtos}{[Link]} Features: automatic website deployment for documentation, CI workflows to replace a \texttt{Makefile} for compiling \texttt{Protocol Buffer} to various common languages, generate corresponding documentation}
\cvitem{Machine learning}{\href{hhttps://github.com/daniel-jakob/Egg_Events_Prediction_ML}{[Link]} Features: \texttt{RandomForestClassifer} machine learning with \texttt{scikit-learn} and \texttt{pandas} libraries, feature extraction and engineering from time series, model training and prediction, data manipulation and visualisation}



%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\newpage
\section{Communication Skills}

\cvitem{Video Editing}{Edited two short videos for college design projects.}
\cvitem{3D Animation}{Created Autodesk  Inventor animations of models with programmatic motions and driven assemblies.}

\cvitem{Presentations}{Presented many small projects and dissertation to peers and professors.}
\cvitem{Technical Writing}{Wrote dozens of technical reports for college projects and my dissertation, including the creation of technical and complex, code-based programmatic diagrams.}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{English}{Mother tongue}{}
\cvitemwithcomment{German}{Proficient}{}
% \cvitemwithcomment{Irish, French}{Basic}{Basic words and phrases only}

%----------------------------------------------------------------------------------------
%	REFERENCES SECTION
%----------------------------------------------------------------------------------------

% \section{References}

% \input{references.tex}

% ----------------------------------------------------------------------------------------
% 	INTERESTS SECTION
% ----------------------------------------------------------------------------------------

% \section{Interests}

% \renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

% \cvlistdoubleitem{Sea swimming}{Instant camera photography}
% \cvlistdoubleitem{Skiing}{Backcountry hiking \& camping}
